Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1113

\end{lem}
\begin{proof}
    Notice that
\begin{align}
\label{eq: upper bound for beta power of z}
    &|z^{\beta}|
    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big|
    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
    \quad z\in \mathbb C_+.
\end{align}
    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
\[
    \gamma(\theta)
    = z_0 (1-\theta) + \theta z_1,
    \quad \theta \in [0,1].
\]
    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
\begin{align}
    |z_0^{1+\beta} - z_1^{1+\beta}|
    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
    \qedhere
\end{align}
\end{proof}
\subsection{}
    Let $X$ be the super OU-process discussed in the previous subsections.
    Its branching mechanism $\psi$ can be extended on $\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$.
    According to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
    Write $\psi_0(z) := \psi(z) + \alpha z$ and $\psi'_0(z) := \psi'(z) + \alpha$.
    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in E$, define $\Psi_0f(x) := \psi_0(x,f(x))$ and $\Psi'_0 f(x) := \psi'_0(x,f(x))$.
    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
    (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ taks values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}

%new added
%end new added
%begin comments
    {\bf Zhenyao: There are notation inconsistency in the Appendix and other sections. Mainly on the branching mechanism: In the appendix, we use
\[
    \psi(x,z)= -\beta(x)z+\alpha(x)z^2 + \int_0^t \dots;
\]
    But in other subsections we use
\[
    \psi(z) = - \alpha z + z^{1+\beta}.
\]
    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.

    Though I recommended all those changes, I did not try to make them in this version (in order to not mess things up). I would like Jianjie to decide which set of notations is better. Overall, I am fine with any set of notations as long as they are consistent with each other and don't raise any confusions.}
%end comments

@@

    Proof of (4): From (1), (2), (3) and Lemma \ref{lem: property of controllable operators}(2) we know that operators
\[
    f
    \mapsto T^{\alpha}_{t-s}\Psi_0(-U_sf)(x),
    \quad 0\leq s\leq t\leq 1
\]
    are uniformly $(1+\beta)$-controllable.
    From Lemma \ref{lem: property of controllable operators}(1) and above we get the desired result.

@@

 In this subsection, for any $\gamma \in (0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$. Denote $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite measures on $\mathbb{R}^d$ with compact support.
\begin{lem}
\label{lem: control pair for P(M>lambda)}
    There is an $(1+\beta)$-control-pair $(R,S)$ such that for each $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$ we have
\[
    \mathbb P_\mu (|M^t_g(0,t)| > \lambda)
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta
    \leq \langle S| g|,\mu\rangle \frac{1}{\lambda^{1+\beta}}.
\]
\end{lem}

\begin{proof}
    Denote by $(R_0,S_0)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}.
    Using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, we have
\begin{align}
    &\mathbb P_\mu (|M^t_g(0,t)| > \lambda)
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{i\theta M_g^t(0,t)}]\Big)d\theta
    = \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1 - \mathbb P_\mu[e^{iM_{(\theta g)}^t(0,t)}]\Big)d\theta
    \\&= \added{\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\Big(1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}\Big) d\theta}
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iT_t^\alpha(\theta g)|,\mu\rangle d\theta
    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta g|,\mu\rangle d\theta
      \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta g|,\mu\rangle d\theta
\end{align}
    To finish the proof we write $R=R_0$ and $S= S_0$.
\end{proof}

\begin{lem}
    There is an $(1+\beta)$-scalable operator $S$ such that for each $g\in \mathcal P$, $\lambda >0$, $\mu\in \mathcal M_c(\mathbb R^d)$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
\[
    \mathbb P_{\mu}(|M^t_g(r,s)|>\lambda)
    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle Sg,\mu\rangle
\]
\end{lem}

\begin{proof}
    Denote by $(R_0,S_0)$ the $(1+\beta)$-control-pair in Lemma \ref{lem: control pair for P(M>lambda)}.
    Then using Markovian property of $(X_t)_{t\geq 0}$ we get
\begin{align}
    &\mathbb P_{\mu}(|M^t_g(r,s)|>\lambda)
    = \mathbb P_\mu \big[\mathbb P_\mu\big(|M_g^t(r,s)|> \lambda\big| \mathscr F_r\big)\big]
    = \mathbb P_\mu \big[\mathbb P_{X_r}(|M^{t-r}_g(0,s-r)|> \lambda)\big]
    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|M^{s-r}_{T^\alpha_{t-s}g}(0,s-r)|> \lambda)\big]
    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \mathbb P_\mu [ \langle S_0Qg,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \langle T_r^\alpha S_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
    \leq e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle QS_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}.
\end{align}
    Note that
\[
    S := \frac{2^{2+\beta}}{2+\beta}QS_0Q
\]
    is an $(1+\beta)$-scalable operator which is independent of the choice of $g,\mu, \lambda, r, s$ and $t$.
\end{proof}

\begin{lem}\label{lem: control of mgtrs}
    For each $g\in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
\[
    \mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big]
    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb)}.
\]
\end{lem}

\begin{proof}
    For each $c>0$ we have
\begin{align}
    &\mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big]
    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|M^t_g(r,s)|>\lambda) d\lambda
    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|M^t_g(r,s)|> \lambda) d\lambda
    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle Sg,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle Sg,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
\end{align}
    Taking $c = e^{(t-s)(\alpha- \kappa_gb)}$ we have
\begin{align}
    &\mathbb P_\mu\big[|M^t_g(r,s)|^{1+\gamma}\big]
    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa_gb)} e^{\alpha r}\Big(1+ \langle Sg,\mu\rangle \frac{1+\gamma}{\beta - \gamma}\Big).
\end{align}
    Note that
\[
    (1+\gamma)(t-s)(\alpha- \kappa_gb) + \alpha r
    \leq t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb).
    \qedhere
\]
\end{proof}
\begin{comment}
\deleted{
\begin{lem}\label{lem: lemma23}
For each $0< \gamma < \beta$ and $\mu \in \mathcal M(\mathbb R^d)$ with compact support, there exists a constant $C_1>0$ such that, for each $t >0$ and $k \in \{0,\dots,\lfloor t \rfloor\}$, we have
\begin{align}
\label{eq: upper bound of 1+gamma moment of Mktg}
    \mathbb P_\mu\big[|M_k^t[g]|^{1+\gamma}\big]
    \leq C_1 C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))k}.
\end{align}
and
\begin{align}
    \mathbb P_\mu\big[|M_t^t[g]|^{1+\gamma}\big]
    \leq C_1 C_g^{1+\gamma}e^{\alpha t}e^{(\alpha \gamma - \kappa b(1+\gamma))t}.
\end{align}
\end{lem}
\begin{proof}
    For each $g \in \mathcal P$, $t\geq 0$, $\gamma \in (0,\beta)$ and $\mu$ with compact support:
\begin{align}
    \mathbb P_\mu\big[|M_t^t[g]|^{1+\gamma}\big]
    = |\langle g_t, \mu\rangle|^{1+\gamma}
    \leq \langle e^{\alpha t} |T_tg|, \mu\rangle^{1+\gamma}
    \leq \langle e^{\alpha t}e^{-\kappa(g)bt}Q[g],\mu\rangle^{1+\gamma}
\leq (e^{\alpha t}e^{-\kappa(g)bt})^{1+\gamma}\langle Q[g],\mu\rangle^{1+\gamma}.
\end{align}
    This proves the Lemma in the case that $M_t^t[g]$.
    So we only have to consider the case when $k \in \{0,\dots,\lfloor t \rfloor\}$.
    Let $c_k=e^{(\alpha-\kappa b)k}$.
    For each $\nu \in \mathcal M(\mathbb R^d)$ with compact support and $0\leq s\leq 1$, denote by $\varphi_{k,\nu,s}$ the characteristic function of $\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle$.

    Step 1. We will show that there exeists an $\tilde R^g_3 \in \mathcal P$ such that for each $\nu \in \mathcal M(\mathbb R^d)$ with compact support and $\lambda > C_g c_k$ we have
\begin{align}
    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle|>\lambda)
    \leq \langle \tilde R^g_3,\nu\rangle \Big(\frac{C_g c_k}{\lambda}\Big)^{1+\beta}, \quad 0\leq s \leq 1.
\end{align}
    In fact, using the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, letting $R^g_2 \in \mathcal P$ and $R^g_3 \in \mathcal P$ be the control functions in Corollary \ref{cor: corollary2} and Corollary \ref{cor: corollary1}, we have
\begin{align}
    &\mathbb{P}_{\nu}(|\langle T_k^{\alpha}g, X_s\rangle-\langle T_{k+s}^{\alpha}g,\nu\rangle|>\lambda)
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1-\varphi_{k,\nu,s}(\theta))d\theta
    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\langle Z_{g_k}(s,\cdot,\theta),\nu\rangle|+|err(k,\nu,\theta)|\big)d\theta
    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\big(|\theta C_g c_k|^{1+\beta}+|\theta C_g c_k|^{1+2\beta}+ |\theta C_g c_k|^{2+2\beta}\big)d\theta \times \langle R^g_2+R^g_3,\nu\rangle
    \\& = \bigg(\frac{2^{2+\beta}}{2+\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{1+\beta}+\frac{2^{2+2\beta}}{2+2\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{1+2\beta} + \frac{2^{3+2\beta}}{3+2\beta}\Big(\frac{C_g c_k}{\lambda}\Big)^{2+2\beta}\bigg) \langle R^g_2+R^g_3,\nu\rangle.
\end{align}
    This implies the desired result in Step 1.

>>>>

\end{lem}
\begin{proof}
    Notice that
\begin{align}
\label{eq: upper bound for beta power of z}
    &|z^{\beta}|
    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big|
    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
    = \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c |z|^{\beta},
    \quad z\in \mathbb C_+.
\end{align}
    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
\[
    \gamma(\theta)
    = z_0 (1-\theta) + \theta z_1,
    \quad \theta \in [0,1].
\]
    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
\begin{align}
    |z_0^{1+\beta} - z_1^{1+\beta}|
    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
    \qedhere
\end{align}
\end{proof}
}
\subsection{}
    Let $X$ be the super OU-process discussed in the \deleted{previous subsections} \added{first subsection}.
    Its branching mechanism $\psi$ can be extended on \deleted{$\mathbb C_+$ by $\psi(z) := -\alpha z + z^{1+\beta}$ for each $z\in \mathbb C_+$} \added{$\mathbb R^d\times \mathbb C_+$ by $\psi(x, z) := -\alpha z + z^{1+\beta}$ for each $x\in \mathbb R^d$ and $z\in \mathbb C_+$}.
    According to the above analysis, \added{for each $x\in \mathbb R^d$}, $\psi\added{(x,\cdot)}$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(\added{x,}z) := -\alpha + (1+\beta)z^{\beta},
    \quad \added{x\in \mathbb R^d}, z\in \mathbb C_+.
\end{equation}
    Write $\psi_0(\added{x,}z) := \psi(\added{x,}z) + \alpha z$ and $\psi'_0(\added{x,}z) := \psi'(\added{x,}z) + \alpha$.
    For each $f\in \mathscr B(\mathbb R^d, \mathbb C_+)$ and $x\in \deleted{E}\added{\mathbb R^d}$, define $\Psi_0f(x) := \psi_0(x,f(x))$ and $\Psi'_0 f(x) := \psi'_0(x,f(x))$.
    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, define $U_tf(x) := \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]|_{\theta = 1}$
    (See the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $-U_tf(x)$ take values in $\mathbb C_+$. Furthermore, we know from Proposition \ref{prop: complex FKPP-equation} that
\begin{align}
\label{eq:chareq2}
    U_tf(x)-\int_0^t T^{\alpha}_{t-s} \Psi_0(-U_sf)(x)ds
    =i T^{\alpha}_t f(x),
    \quad t\in [0,\infty), x\in E, f\in \mathcal P.
\end{align}

    {\bf Zhenyao: There are notation inconsistency in the Appendix and other sections. Mainly on the branching mechanism: In the appendix, we use
\[
    \psi(x,z)= -\beta(x)z+\alpha(x)z^2 + \int_0^t \dots;
\]
    But in other subsections we use
\[
    \psi(z) = - \alpha z + z^{1+\beta}.
\]
    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.}

@@

    Proof of (4): From (1), (2), (3) and Lemma \ref{lem: property of controllable operators}(2) we know that operators
\[
    f
    \mapsto T^{\alpha}_{t-s}\Psi_0(-U_sf)(x),
    \quad 0\leq s\leq t\leq 1
\]
    are uniformly $(1+\beta)$-controllable.
    From \added{\eqref{eq:chareq2},} Lemma \ref{lem: property of controllable operators}(1) and this we get the desired result.

@@

 In this subsection, for any $\gamma \in (0,\beta)$, we want to bound the $(1+\gamma)$-th moment of $\langle g ,X_t \rangle$. Denote $\mathcal{M}_c(\mathbb{R}^d)$ by the space of all finite measures on $\mathbb{R}^d$ with compact support.
\begin{lem}
\label{lem: control pair for P(M>lambda)}
    There is an $(1+\beta)$-control-pair $(R,S)$ such that for each $0\leq t\leq 1$, $g\in \mathcal P$, $\lambda >0$ and $\mu\in \mathcal M_c(\mathbb R^d)$ we have
\[
    \mathbb P_\mu (|\deleted{M^t_g(0,t)} \added{I_0^t[\langle g,X_t\rangle]}| > \lambda)
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta
    \deleted{\leq \langle S| g|,\mu\rangle \frac{2^{2+\beta/(2+\beta)}}{\lambda^{1+\beta}}}.
\]
\end{lem}
\added{
\begin{proof}
    Denote by $(R,S)$ the $(1+\beta)$-control pair for Lemma \ref{lem: upper bound for usgx}(4).
    Using Lemma \ref{lem: estimate of exponential remaining} and the argument in \cite[Proof of Theorem 3.3.6]{Durrett2010Probability}, we have
\begin{align}
    &\big|\mathbb P_\mu (|I_0^t[\langle g,X_t\rangle]| > \lambda)\big|
    \leq \Big|\frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}(1 - \mathbb P_\mu[e^{i\theta I_0^t[\langle g,X_t\rangle]}])d\theta\Big|
    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|1-e^{\langle U_t(\theta g)-iT_t^{\alpha}(\theta g),\mu \rangle}|d\theta
    \leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle |U_t(\theta g) - iT_t^\alpha(\theta g)|,\mu\rangle d\theta
    \\&\leq \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R|\theta g|,\mu\rangle d\theta.
      \qedhere
\end{align}
\end{proof}
}

{\bf Zhenyao: I will change $M_g^t(a,b)$ to $I_a^b[\langle g,X_t\rangle]$ without mention. Here ``I'' means incremental.}

\begin{lem}
    There is an $(1+\beta)$-scalable operator $S$ such that for each $g\in \mathcal P$, $\lambda >0$, $\mu\in \mathcal M_c(\mathbb R^d)$ and $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
\[
    \mathbb P_{\mu}(|\added{I_r^s[\langle g, X_t\rangle]}|>\lambda)
    \leq \frac{ 1}{\lambda^{1+\beta}} e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle S\added{Q}g,\mu\rangle.
\]
\end{lem}

\begin{proof}
    Denote by $(R_0,S_0)$ the $(1+\beta)$-control-pair in Lemma \ref{lem: control pair for P(M>lambda)}.
    Then using Markovian property of $(X_t)_{t\geq 0}$ we get
\added{
\begin{align}
    &\mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda)
    = \mathbb P_\mu \big[\mathbb P_\mu[|\langle T_{t-s}^\alpha g, X_{s}\rangle - \langle T_{t-r}^\alpha g, X_{r}\rangle|> \lambda\big| \mathscr F_r]\big]
    \\&= \mathbb P_\mu \big[\mathbb P_{X_r}(|\langle T_{t-s}^\alpha g, X_{s-r}\rangle - \langle T_{t-r}^\alpha g, X_{0}\rangle|> \lambda)\big]
    = \mathbb P_\mu \big[\mathbb P_{X_r}(|I_0^{s-r}[\langle T_{t-s}^\alpha g, X_{s-r}\rangle] |> \lambda)\big]
    \\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta T^\alpha_{t-s}g|,X_r\rangle d\theta \Big]
    \leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle R_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
	\\&\leq \mathbb P_\mu \Big[ \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}\langle S_0|\theta e^{(t-s)(\alpha- \kappa_gb)}Qg|,X_r\rangle d\theta \Big]
    = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \mathbb P_\mu [ \langle S_0Qg,X_r\rangle ] \frac{\lambda}{2}\int_{-2/\lambda}^{2/\lambda}|\theta|^{1+\beta}d\theta
    \\& = e^{(1+\beta)(t-s)(\alpha- \kappa_gb)} \langle T_r^\alpha S_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}
    \leq e^{(1+\beta)(t-s)(\alpha- \kappa_gb)+ \alpha r} \langle QS_0Qg,\mu\rangle  \frac{2^{2+\beta}}{2+\beta}\frac{1}{\lambda^{1+\beta}}.
\end{align}
}
    Note that
\[
    S := \frac{2^{2+\beta}}{2+\beta}QS_0\deleted{Q}
\]
    is an $(1+\beta)$-scalable operator which is independent of the choice of $g,\mu, \lambda, r, s$ and $t$.
\end{proof}

\begin{lem}\label{lem: control of mgtrs}
    For each $g\in \mathcal P$, $\mu \in \mathcal M_c(\mathbb{R}^d)$ and $0<\gamma < \beta$, there exists a constant $C>0$ such that for each $0\leq r\leq s\leq t$ with $s-r \leq 1$ we have
\[
    \mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
    \leq C e^{t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb)}.
\]
\end{lem}

\begin{proof}
	\added{Let $S$ be the $(1+\beta)$-scalable operator in the previous Lemma.}
    For each $c>0$ we have
\begin{align}
    &\mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
    = (1+\gamma)\int_0^\infty \lambda^{\gamma} \mathbb P_{\mu}(|I_r^s[\langle g, X_t\rangle]|>\lambda) d\lambda
    \\&\leq (1+\gamma)\int_0^c \lambda^{\gamma} d\lambda +(1+\gamma)\int_c^\infty \lambda^{\gamma}\mathbb P_\mu(|I_r^s[\langle g, X_t\rangle]|> \lambda) d\lambda
    \\& \leq c^{1+\gamma} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle S\added{Q}g,\mu\rangle  (1+\gamma)\int_c^\infty \frac{1}{\lambda^{1+(\beta-\gamma)}}d\lambda
    \\&\leq c^{1+\gamma} e^{\alpha r} + e^{(1+\beta)(t-s)(\alpha- \kappa_gb) + \alpha r} \langle S\added{Q}g,\mu\rangle   \frac{1+\gamma}{\beta - \gamma} \frac{1}{c^{\beta - \gamma}}.
\end{align}
    Taking $c = e^{(t-s)(\alpha- \kappa_gb)}$ we have
\begin{align}
    &\mathbb P_\mu\big[|I_r^s[\langle g, X_t\rangle]|^{1+\gamma}\big]
    \leq e^{(1+\gamma)(t-s)(\alpha- \kappa_gb)} e^{\alpha r}\Big(1+ \langle SQg,\mu\rangle \frac{1+\gamma}{\beta - \gamma}\Big).
\end{align}
    Note that
\[
    (1+\gamma)(t-s)(\alpha- \kappa_gb) + \alpha r
    \leq t\alpha+(t-s) (\gamma\alpha- (1+\gamma)\kappa_gb).
    \qedhere
\]
\end{proof}
\begin{comment}
\end{comment}
    \deleted{As $\langle g,X_t\rangle,~g\in \mathcal{P}$ is the sum of $M_g^t(k,k+1), k=0,1,...,\lfloor t\rfloor$ and $M_g^t(\lfloor t\rfloor, t)$. We obtain the following lemma.}

\begin{lem}
\label{lemma24}
    For each $0 < \gamma < \beta$ and $\mu\in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$ there exists a constant $C>0$ such that for each $t\geq 0$:
\begin{itemize}
\item[(1)]
    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{(\alpha-\kappa_g b)t}$ provided $\alpha\gamma > \kappa_g (1+\gamma)b$.
\item[(2)]
    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C te^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma = \kappa_g (1+\gamma)b$.
\item[(3)]
    $\|\langle g,X_t\rangle\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{\frac{\alpha}{1+\gamma}t}$ provided $\alpha\gamma < \kappa_g (1+\gamma)b$.
\end{itemize}
\end{lem}
\begin{proof}
    Fix $\gamma \in (0,\beta)$ and $\mu \in \mathcal M_c(\mathbb R^d)$ and $g\in \mathcal P$.
    Let $C$ be the constant in Lemma \ref{lem: control of mgtrs}.
    Using the triangle inequality,
\begin{align}
    \|\langle g,X_t\rangle\|_{\mathbb P_\mu;1+\gamma}
    &\leq \sum_{k=0}^{\lfloor t\rfloor - 1}\big\| I_{t-k-1}^{t-k}[\langle g,X_t\rangle] \big\|_{\mathbb P_\mu;1+\gamma}+\big\| I_{0}^{t-\lfloor t \rfloor}[\langle g,X_t\rangle]  \big\|_{\mathbb P_\mu;1+\gamma}
    \\ &\leq C e^{\frac{\alpha}{1+\gamma}t}\sum_{k=0}^{\lfloor t\rfloor} e^{\frac{\gamma\alpha-\kappa_g (1+\gamma)b}{1+\gamma} k} .
\end{align}
    By calculating the sum on the right, we get the desired result.
\end{proof}

\subsection{Martingales}
    In this subsection, we will prove the almost sure and $L^{1+\gamma}(\mathbb{P}_{\mu})$ convergence of some martingales with $0<\gamma<\beta$. Recall that $L$ is the infinitesimal generator of OU-process. Let $a\in \mathbb{R}$ and $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$ ,we define that
\begin{align}
\label{defmartingale}
    M_t^{f,a}:=e^{-(\alpha-ab)t}\langle f,X_t\rangle-\int_0^t e^{-(\alpha-ab)s}\langle (L+ab)f, X_s\rangle~ ds.
\end{align}
{\bf Zhenyao: we should show that it is well defined.}
    The following lemma says that $\{M_t^{f,a}: t\geq 0\}$ is a martingale corresponding to the $\sigma$-algebra \added{$\{\mathscr{F}_t\}_{t\geq 0}$}.
{\bf Zhenyao: I changed all $\mathcal F$ to $\mathscr F$ without mention below. I want to use mathscr for $\sigma$-fields and mathcal for function classes.}
\begin{lem}
\label{lemma25}
    Let $a\in \mathbb R$ and $f\in \mathcal{P}\cap C^2(\mathbb{R}^d)$ such that $Lf \in \mathcal{P}$. Then the process $(M_t^{f,a})_{t\geq 0}$ is an $(\mathscr F_t)$-martingale.
\end{lem}
\begin{proof}
    Write $\bar{f}=(L+ab)f$. According to \cite[Theorem A.55]{Li2011Measure-valued}, we have
\begin{align}\label{Theorem55}
    T_t^{ab}f(x)= f(x)+\int_0^t T_s^{ab}\bar{f}(x)~ds,\quad t\geq 0,x\in \mathbb{R}^d.
\end{align}
Let $0\leq s\leq t$,
\begin{align}
\label{martingale1}
    &\mathbb{P}_{\mu}[M_t^{f,a}|\mathscr{F}_s]
    =e^{-(\alpha-ab)t}\mathbb{P}_{\mu}\left[\langle f,X_t\rangle|\mathscr{F}_s\right]-\mathbb{P}_{\mu}\Big[\int_0^t e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du\Big|\mathscr{F}_s\big]
    \\&=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-\int_0^s e^{-(\alpha-ab)u}\langle \bar{f}, X_u\rangle~ du -\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du.
\end{align}
    Using \eqref{Theorem55} and Fubini's theorem, we have
\begin{align}
    &\int_s^t e^{-(\alpha-ab)u}\langle T_{u-s}^{\alpha} \bar{f},X_s\rangle~ du=e^{-(\alpha-ab)s}\int_s^t\langle T_{u-s}^{ab}\bar{f},X_s\rangle~du\\
    &=e^{-(\alpha-ab)s}\Big\langle\int_0^{t-s}T_{u}^{ab}\bar{f}~du,X_s\Big\rangle=e^{-(\alpha-ab)s}\left(\langle T_{t-s}^{ab}f,X_s\rangle-\langle
    f,X_s\rangle\right)\\
    &=e^{-(\alpha-ab)t}\langle T_{t-s}^{\alpha}f, X_s\rangle-e^{-(\alpha-ab)s}\langle
    f,X_s\rangle.
\end{align}
   Using this and \eqref{martingale1}, we get the desired result.
\end{proof}
